Parallel air palletization and tour planning for simultaneous pickup and delivery

### 2022-11-24 latex/comp_or.tex
Algorithms shape updated

\begin{algorithm}[H]
	\caption{$ACLP+RPDP (scenario,volume)$}  \label{alg:main}
	\begin{algorithmic}[1]
		\State Let $L, M, C$ be according to $scenario$ \label{main:LMC}
		\State $N \gets ItemsGeneration(scenario,volume)$ \label{main:items}
		\For {each $method$}

			\State $numProcs \gets $, the number of parallel processes to be used

			\For {each $\pi \in S_K$} \label{main:loop1}
				\State $f_{\pi} \gets SolveTour(\pi, L, M, C, N, method, numProcs )$ \label{main:method}
			\EndFor \label{main:loop2}
			\State $answer[scenario,volume,method] \gets \max f$ \label{main:f}
		\EndFor
		\State $ {\bf return}\ answer$
	\end{algorithmic}
\end{algorithm}

@@

\begin{algorithm}[H]
	\caption{$SolveTour(\pi, L, M, C, N, method, numProcs)$}  \label{alg:tour}

@@

		\State $\pi(0) \gets 0$ \label{tour:pi1}
		\State $\pi(K+1) \gets 0$ \label{tour:pi2}
		\State $score \gets 0$ \label{tour:score}
		\State $cost \gets 0$ \label{tour:cost}
		\For {$k\gets0$ to $K$} \label{tour:loop1}		
			\For{$i \gets 1$ to $m$}
				\State $p_i.to[k] \gets -1$ \label{tour:-1}
			\EndFor	
			\If {$k = 0$}
				\State $L_0 \gets L$
				\State Let $G_1(M \cup N_0, \varnothing)$ \label{tour:g11}
			\Else
				\State $L_k \gets L_k - \pi(k)$  \label{tour:lk1}			
				\State $Q_{\pi(k)}, E^Q_{\pi(k)}, M \gets UpdateConsolidated(\pi(k))$ \label{tour:dest}			
				\State Let $G_1(M \cup N_{\pi(k)} \cup Q_{\pi(k)}, E^Q_{\pi(k)})$ \label{tour:g12}
			\EndIf  \label{tour:lk2}	
			\State $M \gets SetPalletsDestination( \pi(k) )$ \label{tour:dest2}		
			\State $G_2 \gets SolveNode(method, \pi(k), G_1, numProcs)$ \label{tour:node}
			\State $s, \epsilon \gets ScoreAndDeviation(\pi(k), G_2)$ \label{tour:analyse}
			\State $score \gets score + s$ \label{tour:score2}
			\State $cost \gets cost + c_{\pi(k),\pi(k+1)} * (1 + c_g * |\epsilon|)$ \label{tour:cost2} 
		\EndFor  \label{tour:loop2}
		\State $ {\bf return}\ score / cost$ \label{tour:f}

@@

	\caption{ $SolveNode(mpACO, k, G, numProcs)$ } \label{alg:aco}
	\begin{algorithmic}[1]
		\State Let $G(V_k, E^Q_k)$ \Comment{This is a partial solution with only consolidated on board}
		\State $G^*(V_k, E^{N*}_k \cup E^Q_k), \_ \gets Greedy(k, G, 0.9)$  \label{aco:greedy} \Comment{This partial solution is completed by a greedy algorithm}
		\State $G^+(V_k, E^{N+}_k \cup E^Q_k) \gets G^*(V_k,E^{N*}_k \cup E^Q_k)$
		\State $A \gets numProcs$ \label{aco:numProcs}
		\State $ga^k_{ij}   \gets 0$, $1 \leq i \leq m$, $1 \leq j \leq n_k$  \label{aco:init1}
		\State $\tau^k_{ij} \gets 1$, $1 \leq i \leq m$, $1 \leq j \leq n_k$   \label{aco:init2}
		\State $\alpha    \gets 1.0$ \label{aco:alpha}
		\State $\beta     \gets 4.0$ \label{aco:beta}
		\State $\rho      \gets 0.2$ \label{aco:rho}
		\State $stagnant \gets 0$
		\While{ $stagnant < 3$ } \label{aco:while}

@@

			\While{$runtime < 0.7s$ {\bf and} $counter > 0$} \label{aco:while2}

				\State $G^{a} \gets AntsQueue.Pop()$	
				\If{$f_s(G^{a}) > f_s(G^{+})$}
					\State $G^+(V_k, E^{N+}_k \cup E^Q_k) \gets G^a(V_k, E^{Na}_k \cup E^Q_k)$ 
				\EndIf

@@

			\If{$f_s(G^+) > f_s(G^*)$} \label{aco:best1}
				\State $stagnant \gets 0$
				\State $G^*(V_k, E^{N*}_k \cup E^Q_k) \gets G^+(V_k, E^{N+}_k \cup E^Q_k)$		
			\Else
				\State $stagnant \gets stagnant + 1$ 
			\EndIf
			\For{all $\tau^k_{ij}$} 
				\State $\tau^k_{ij} \gets (1-\rho)\tau^k_{ij}$ \label{aco:rho2}
				\State $\tau^k_{ij} \gets \tau^k_{ij} + \Delta\tau$ \label{aco:phero2}
				\State $ga^k_{ij} \gets (\tau^k_{ij})^\alpha + (\theta^k_{ij})^\beta$ \label{aco:ga2}				
			\EndFor	
		\EndWhile	
		\State ${\bf return}$ $G^*(V_k, E^{N*}_k \cup E^Q_k)$		
	\end{algorithmic}
\end{algorithm}

@@

\begin{algorithm}[H]
	\caption{ $Greedy(k, G, limit)$}  \label{alg:greedy}

	\begin{algorithmic}[1]
		\State Let $G(V_k, E^Q_k)$

@@

		\For{$q \gets 1$ to $m$}
			\If{$(p_i, a_q^k) \in E^Q_k$} 
				\State $volume[i] \gets volume[i] + a_q^k.v$ 
			\EndIf		
		\EndFor

		\For {each $e_{ij}^k$ in non-ascending order of $\theta^k_{ij}$}
			\If{($E^N_k \cup \{e_{ij}^k\}$ is feasible) {\bf and} ($volume[i] \leq p_i.v \times limit$)} 
				\State $E^N_k \gets E^N_k \cup \{e_{ij}^k\}$ 
				\State $volume[i] \gets volume[i] + t_j^k.v$
				\State $\eta_1[i] \gets \eta_1[i] + 1$ 	
			\EndIf
		\EndFor
		\State ${\bf return}\ G(V_k, E^N_k \cup E^Q_k),\ \eta_1$

@@

\begin{algorithm}[H] 
	\caption{ $AntSolve(G^+,\ AntsQueue,\ ga^k_{ij})$ } \label{alg:AntSolve}
	\begin{algorithmic}[1]
		\State $G^a(V_k, E^{Na}_k \cup E^Q_k) \gets G^+(V_k, E^{N+}_k \cup E^Q_k)$
		\State $E \gets \{ (p_i,t^k_j) \mid (p_i,t^k_j) \not\in E^{Na}_k \}$ \label{AntSolve:neighborhood}
		\While{$|E| > 0$} \label{AntSolve:not_empty}
			\State $e \gets Roulette(E)$ biased through $ga^k_{ij}$  \label{AntSolve:roulette}
			\State $E \gets E - \{e\}$		
			\If{$E^{Na}_k \cup \{e\}$ is feasible}
				\State $ E^{Na}_k \gets E^{Na}_k \cup \{e\} $ \label{AntSolve:ant}
			\EndIf	
		\EndWhile

\State $\tau^k_{ij} \gets (1-\rho)\tau^k_{ij}$ \label{AntSolve:rho}
\State $\tau^k_{ij} \gets \tau^k_{ij} + \Delta\tau$ \label{AntSolve:phero}
\State $ga^k_{ij} \gets (\tau^k_{ij})^\alpha + (\theta^k_{ij})^\beta$ \label{AntSolve:ga}

		\State $AntsQueue \gets AntsQueue \cup G^a(V_k, E^{Na}_k \cup E^Q_k)$ \label{AntSolve:put_in_queue}
	\end{algorithmic}
\end{algorithm}

Algorithm \ref{alg:AntSolve}, which will be executed by a child parallel process, receives an initial and poor solution ($G^+(V_k, E^{N+}_k \cup E^Q_k)$) generated greedily to be completed and improved by {\it mpACO}.

@@

While the neighborhood is not empty (\ref{AntSolve:not_empty}), choose an edge (\ref{AntSolve:roulette}), delete it from the neighborhood and include it in the solution, if feasible (\ref{AntSolve:ant}).

Finally, put the solution in the queue (\ref{AntSolve:put_in_queue}) to be retrieved by the main process.

@@

\begin{algorithm}[H]
	\caption{ $SolveNode(mpShims, k, G, numProcs)$}  \label{alg:mpshims}
	\begin{algorithmic}[1]

@@

		\While{$runtime < 0.7s$ {\bf and} $counter > 0$}

			\State $G \gets shimsQueue.Pop()$	\label{mpshims:wait}
			\If{$f_s(G) > f_s(G^*)$}
				\State $G^* \gets G$ 
			\EndIf

@@

		\State ${\bf return}$ $G^*(V_k, E^N_k \cup E^Q_k)$ \label{mpshims:return}
	\end{algorithmic}
\end{algorithm}

@@

\begin{algorithm}[H]
	\caption{ $shimsSolve(G,\ M,\ shimsQueue,\ limit,\ E)$}  \label{alg:shimsSolve}
	\begin{algorithmic}[1]

@@

@@

\begin{algorithm}[H]
	\caption{ $getBestShims(i,\ \eta_1,\ \eta_2,\ E,\ k,\ slack)$ }  \label{alg:getBestShims}
	\begin{algorithmic}[1]

@@

		\State ${\bf return}$ $sh_{best}$

@@

Observing Figure \ref{fig:scenario1data20}, it may be noticed that the best number of processes for {\it Scenario 1} (the closest to the {\it Utopia}) is \textbf{6}. For {\it Scenario 2}, the best number is \textbf{4}. Table \ref{tab:numProcs} presents all methods, volumes percentages and scenarios numbers of best parallel processes to be run to solve all tours.

@@

\begin{algorithm}[H]
	\caption{$getBestNPP(scores, runtimes, procs)$}  \label{alg:bestnum}
	\begin{algorithmic}[1]
		\State $maxS   \gets max(scores)$
		\State $minS   \gets min(scores)$
		\State $maxR \gets max(runtimes)$
		\State $minR \gets min(runtimes)$

@@

		\For{$i \in |scores|$}
			\State $y = ( maxS - scores[i] )\ /\ (maxS   - minS  )$, the Y axis leg of Figure \ref{fig:scenario1data20}
			\State $x = ( runtimes[i] - minR )\ /\ (maxR - minR)$. the X axis leg
			\State $h = \sqrt{x^2 + y^2}$, the hypotenuse, distance from {\it Utopia}
			\If{$minD$ > $h$}
				\State $minD \gets h$
				\State $bestNPP \gets procs[i]$
			\EndIf

@@

		\State ${\bf return}$ $bestNPP$
	\end{algorithmic}
\end{algorithm}

@@

		\multirow{4}{*}{$1.2$} &\multirow{2}{*}{\it {mpShims}} & $f$                & 5.70  & 3.09  & 2.94  & 2.90  & 2.79  & 5.70  & 0.91  \\%2312
		                       &                               & {\bf run-time (s)} & 1     & 3     & 7     & 26    & 97    & 267   & 70  \\%390
		                       \cmidrule{2-10}
		                       &\multirow{2}{*}{\it {mpACO}}   & $f$                & 6.42  & 3.78  &  3.19 & 3.17  & 2.97  & 5.87  & 1.00  \\ %2540
                               &                               & {\bf run-time (s)} & 16    & 282   &  314  & 1334  & 6945  & 18883 & 1  \\ %27162
		\midrule
		\multirow{4}{*}{$1.5$} &\multirow{2}{*}{\it {mpShims}} & $f$                & 8.15  & 4.22  & 4.40  & 4.01  & 3.51  & 7.08  &   \\
		                       &                               & {\bf run-time (s)} & 1     & 5     & 12    & 45    & 244   & 737   &   \\
		\cmidrule{2-10}
		                       &\multirow{2}{*}{\it {mpACO}}   & $f$                &&&&&&&\\
		                       &                               & {\bf run-time (s)} &&&&&&&\\
		\midrule
		\multirow{4}{*}{$2.0$} &\multirow{2}{*}{\it {mpShims}} & $f$                & 11.31 & 6.29  & 5.54  & 5.83  & 5.05  & 10.63 &   \\
		                       &                               & {\bf run-time (s)} & 2     & 14    & 34    & 106   & 477   & 2417  &   \\
		\cmidrule{2-10}
		                       &\multirow{2}{*}{\it {mpACO}}   & $f$                &&&&&&&\\
		                       &                               & {\bf run-time (s)} &&&&&&&\\

>>>>

\begin{algorithm}[H]
	\caption{Solves ACLP+RPDP for a scenario with certain volume surplus (1.2, 1.5, or 2.0)}  \label{alg:main}
	\begin{algorithmic}[1]

		\Procedure{$ACLP+RPDP$}{$scenario,\ surplus,\ numProcs$}

		\State Let $L, M, C$ be according to $scenario$ \label{main:LMC}
		\State $N \gets ItemsGeneration(scenario,\ surplus)$ \label{main:items}
		\For {each $method$}

			\For {each $\pi \in S_K$} \label{main:loop1}
				\State $f_{\pi} \gets SolveTour(\pi, L, M, C, N, method, numProcs )$ \label{main:method}
			\EndFor \label{main:loop2}
			\State $answer[scenario,surplus,method] \gets \max f$ \label{main:f}
		\EndFor

		\Return $answer$

		\EndProcedure
	\end{algorithmic}
\end{algorithm}

@@

\begin{algorithm}[H]
	\caption{ Solves the sequence of nodes in the tour indexed by $\pi$ }  \label{alg:tour}

@@

		\Procedure{$SolveTour$}{$\pi, L, M, C, N, method, numProcs$}

		\State $\pi(0) \gets 0$ \label{tour:pi1}
		\State $\pi(K+1) \gets 0$ \label{tour:pi2}
		\State $score \gets 0$ \label{tour:score}
		\State $cost \gets 0$ \label{tour:cost}
		\For {$k\gets0$ to $K$} \label{tour:loop1}		
			\For{$i \gets 1$ to $m$}
				\State $p_i.to[k] \gets -1$ \label{tour:-1}
			\EndFor	
			\If {$k = 0$}
				\State $L_0 \gets L$
				\State Let $G_1(M \cup N_0, \varnothing)$ \label{tour:g11}
			\Else
				\State $L_k \gets L_k - \pi(k)$  \label{tour:lk1}			
				\State $Q_{\pi(k)}, E^Q_{\pi(k)}, M \gets UpdateConsolidated(\pi(k))$ \label{tour:dest}			
				\State Let $G_1(M \cup N_{\pi(k)} \cup Q_{\pi(k)}, E^Q_{\pi(k)})$ \label{tour:g12}
			\EndIf  \label{tour:lk2}	
			\State $M \gets SetPalletsDestination( \pi(k) )$ \label{tour:dest2}		
			\State $G_2 \gets SolveNode(method, \pi(k), G_1, numProcs)$ \label{tour:node}
			\State $s, \epsilon \gets ScoreAndDeviation(\pi(k), G_2)$ \label{tour:analyse}
			\State $score \gets score + s$ \label{tour:score2}
			\State $cost \gets cost + c_{\pi(k),\pi(k+1)} * (1 + c_g * |\epsilon|)$ \label{tour:cost2} 
		\EndFor  \label{tour:loop2}
		\Return $score / cost$ \label{tour:f}

		\EndProcedure

@@

	\caption{ Solves a node with the {\it mpACO} method } \label{alg:aco}
	\begin{algorithmic}[1]

		\Procedure{$SolveNode$}{$mpACO, k, G, numProcs$}

		\State Let $G(V_k, E^Q_k)$ \Comment{This is a partial solution with only consolidated on board}
		\State $G^*(V_k, E^{N*}_k \cup E^Q_k), \_ \gets Greedy(k, G, 0.9)$  \label{aco:greedy} \Comment{This partial solution is completed by a greedy algorithm}
		\State $G^+(V_k, E^{N+}_k \cup E^Q_k) \gets G^*(V_k,E^{N*}_k \cup E^Q_k)$
		\State $A \gets numProcs$ \label{aco:numProcs}
		\State $ga^k_{ij}   \gets 0$, $1 \leq i \leq m$, $1 \leq j \leq n_k$  \label{aco:init1}
		\State $\tau^k_{ij} \gets 1$, $1 \leq i \leq m$, $1 \leq j \leq n_k$   \label{aco:init2}
		\State $\alpha    \gets 1.0$ \label{aco:alpha}
		\State $\beta     \gets 4.0$ \label{aco:beta}
		\State $\rho      \gets 0.2$ \label{aco:rho}
		\State $stagnant \gets 0$
		\While{ $stagnant < 3$ } \label{aco:while}

@@

			\While{$counter > 0$} \label{aco:while2}

				\State $G^{a} \gets \varnothing$

				\While{$runtime < 0.7s$} \Comment{Wait until there is a solution in the queue}

					\State $G^{a} \gets AntsQueue.Pop()$

					\If{$G^{a} \ne \varnothing$}				
						\Break
					\EndIf

				\If{$f_s(G^{a}) > f_s(G^{+})$}
					\State $G^+(V_k, E^{N+}_k \cup E^Q_k) \gets G^a(V_k, E^{Na}_k \cup E^Q_k)$ 
				\EndIf

@@

			\If{$f_s(G^+) > f_s(G^*)$} \label{aco:best1}
				\State $stagnant \gets 0$
				\State $G^*(V_k, E^{N*}_k \cup E^Q_k) \gets G^+(V_k, E^{N+}_k \cup E^Q_k)$		
			\Else
				\State $stagnant \gets stagnant + 1$ 
			\EndIf
			\For{all $\tau^k_{ij}$} 
				\State $\tau^k_{ij} \gets (1-\rho)\tau^k_{ij}$ \label{aco:rho2}
				\State $\tau^k_{ij} \gets \tau^k_{ij} + \Delta\tau$ \label{aco:phero2}
				\State $ga^k_{ij} \gets (\tau^k_{ij})^\alpha + (\theta^k_{ij})^\beta$ \label{aco:ga2}				
			\EndFor	
		\EndWhile	
		\Return $G^*(V_k,\ E^{N*}_k \cup E^Q_k)$

		\EndProcedure		
	\end{algorithmic}
\end{algorithm}

@@

\begin{algorithm}[H]
	\caption{Mount a greedy solution until the volume limit for each pallet}  \label{alg:greedy}

		\Procedure{$Greedy$}{$k, G, limit$}

		\State Let $G(V_k, E^Q_k)$

@@

		\For{$q \gets 1$ to $m$}
			\If{$(p_i, a_q^k) \in E^Q_k$} 
				\State $volume[q] \gets volume[q] + a_q^k.v$ 
			\EndIf		
		\EndFor

		\For {each $e_{ij}^k$ in non-ascending order of $\theta^k_{ij}$}
			\If{($E^N_k \cup \{e_{ij}^k\}$ is feasible) {\bf and} ($volume[i] \leq p_i.v \times limit$)} 
				\State $E^N_k \gets E^N_k \cup \{e_{ij}^k\}$ 
				\State $volume[i] \gets volume[i] + t_j^k.v$
				\State $\eta_1[i] \gets \eta_1[i] + 1$ 	
			\EndIf
		\EndFor

		\Return $G(V_k, E^N_k \cup E^Q_k),\ \eta_1$ \Comment{return the solution and the last item indexes array }

		\EndProcedure

@@

\begin{algorithm}[H] 
	\caption{Each ant solves a node in parallel} \label{alg:AntSolve}
	\begin{algorithmic}[1]

		\Procedure{$AntSolve$}{$G^+,\ AntsQueue,\ ga^k_{ij})$}

		\State $G^a(V_k, E^{Na}_k \cup E^Q_k) \gets G^+(V_k, E^{N+}_k \cup E^Q_k)$
		\State $E \gets \{ (p_i,t^k_j) \mid (p_i,t^k_j) \not\in E^{Na}_k \}$ \label{AntSolve:neighborhood}
		\While{$|E| > 0$} \label{AntSolve:not_empty}

			\State $e \gets Roulette(E)$ biased through $ga^k_{ij}$  \label{AntSolve:roulette}
			\State $E \gets E - \{e\}$		
			\If{$E^{Na}_k \cup \{e\}$ is feasible}
				\State $ E^{Na}_k \gets E^{Na}_k \cup \{e\} $ \label{AntSolve:ant}
			\EndIf

%\For{$\tau^k_{ij}, \theta^k_{ij} \in E^{Na}_k$}
%\State $\tau^k_{ij} \gets (1-\rho)\tau^k_{ij}$ \label{AntSolve:rho}
%\State $\tau^k_{ij} \gets \tau^k_{ij} + \Delta\tau$ \label{AntSolve:phero}  \Comment{$\Delta\tau \gets$ Equation \ref{eq:delta_tau}}
%\State $ga^k_{ij} \gets (\tau^k_{ij})^\alpha + (\theta^k_{ij})^\beta$ \label{AntSolve:ga}		
%\EndFor

		\State $AntsQueue \gets AntsQueue \cup G^a(V_k,\ E^{Na}_k \cup E^Q_k)$ \label{AntSolve:put_in_queue}

		\EndProcedure
	\end{algorithmic}
\end{algorithm}

Algorithm \ref{alg:AntSolve}, which will be executed by a child parallel process, receives an initial and poor solution $G^+(V_k, E^{N+}_k \cup E^Q_k)$ generated greedily to be completed and improved by {\it mpACO}.

@@

While the neighborhood is not empty (line \ref{AntSolve:not_empty}), choose an edge (line \ref{AntSolve:roulette}), delete it from the neighborhood and include it in the solution, if feasible (line \ref{AntSolve:ant}).

Finally, put the solution in the queue (line \ref{AntSolve:put_in_queue}) to be retrieved by the main process.

%Note that $ga^k_{ij}$ is updated by each parallel ant, which may influence the solution of the others during run-time. This fully connected topology may increase run-time due to the overhead in communications handled by {\it Python API Multiprocessing} but it is expected that this will yield better solutions.

@@

\begin{algorithm}[H]
	\caption{Solve a node with {\it mpShims}}  \label{alg:mpshims}
	\begin{algorithmic}[1]

		\Procedure{$SolveNode$}{$mpShims, k, G, numProcs$}

@@

		\While{$counter > 0$}

			\State $G \gets \varnothing$

			\While{$runtime < 0.7s$} \Comment{Wait until there is a solution in the queue}

			\State $G \gets shimsQueue.Pop()$
				\If{$G \ne \varnothing$}
					\Break
				\EndIf
			\EndWhile

			\If{$f_s(G) > f_s(G^*)$}
				\State $G^* \gets G$ 
			\EndIf
			\State $counter \gets counter - 1$

@@

		\Return $G^*(V_k, E^N_k \cup E^Q_k)$ \label{mpshims:return}

		\EndProcedure
	\end{algorithmic}
\end{algorithm}

@@

\begin{algorithm}[H]
	\caption{Shims solving method to be run in parallel}  \label{alg:shimsSolve}
	\begin{algorithmic}[1]

		\Procedure{$shimsSolve$}{$G,\ M,\ shimsQueue,\ limit,\ E$}

@@

		\EndProcedure

@@

\begin{algorithm}[H]
	\caption{Get the best shims of edges that fills each pallet gap}  \label{alg:getBestShims}
	\begin{algorithmic}[1]

		\Procedure{$getBestShims$}{$i,\ \eta_1,\ \eta_2,\ E,\ k,\ slack$}

@@

		\Return $sh_{best}$

		\EndProcedure

@@

Observing Figure \ref{fig:scenario1data20}, it may be noticed that the best number of processes for {\it Scenario 1} solved with {\it mpShims} (the closest to the {\it Utopia}) is \textbf{6}. Solved with {\it mpACO}, the best number is \textbf{8}. Table \ref{tab:numProcs} presents all methods, volumes percentages and scenarios numbers of best parallel processes to be run to solve all tours.

@@

\begin{algorithm}[H]
	\caption{Get the best number of parallel processes}  \label{alg:bestnum}
	\begin{algorithmic}[1]

		\Procedure{$getBestNPP$}{$scores,\ runtimes,\ procs$}

		\State $maxS   \gets max(scores)$
		\State $minS   \gets min(scores)$
		\State $maxR \gets max(runtimes)$
		\State $minR \gets min(runtimes)$

@@

		\For{$i \in |scores|$}
			\State $y = ( maxS - scores[i] )\ /\ (maxS   - minS  )$ \Comment{the Y axis leg}
			\State $x = ( runtimes[i] - minR )\ /\ (maxR - minR)$ \Comment{the X axis leg}
			\State $h = \sqrt{x^2 + y^2}$  \Comment{distance from {\it Utopia}}
			\If{$minD$ > $h$}
				\State $minD \gets h$
				\State $bestNPP \gets procs[i]$
			\EndIf

@@

		\Return $bestNPP$

		\EndProcedure
	\end{algorithmic}
\end{algorithm}

@@

		\multirow{6}{*}{$1.2$} &\multirow{2}{*}{ $mpShims^{0.7s}$}& $f$                & 5.70  & 3.09  & 2.94  & 2.90  & 2.79  & 5.70  & 0.91  \\%2312
		                       &                                 & {\bf run-time (s)} & 1     & 3     & 7     & 26    & 97    & 267   & 70  \\%390
		                       \cmidrule{2-10}
		                       &\multirow{2}{*}{ $mpACO^{60s}$}   & $f$                & 6.42  & 3.78  &  3.19 & 3.17  & 2.97  & 5.87  & 1.00  \\ %2540
                               &                                 & {\bf run-time (s)} & 16    & 282   &  314  & 1334  & 6945  & 18883 & 1  \\ %27162
		\cmidrule{2-10}		                       
							   &\multirow{2}{*}{ $mpACO^{0.7s}$}  & $f$                &&&&&&&\\
							   &                                 & {\bf run-time (s)} &&&&&&&\\                               
		\midrule
		\multirow{6}{*}{$1.5$} &\multirow{2}{*}{ $mpShims^{0.7s}$}& $f$                & 8.15  & 4.22  & 4.40  & 4.01  & 3.51  & 7.08  &   \\
		                       &                                 & {\bf run-time (s)} & 1     & 5     & 12    & 45    & 244   & 737   &   \\
		\cmidrule{2-10}
		                       &\multirow{2}{*}{ $mpACO^{60s}$}   & $f$                & 9.50  & 5.01  & 4.60  & 4.28  &&&\\
		                       &                                 & {\bf run-time (s)} & 9     & 344   & 787   & 1525  &&&\\
		\cmidrule{2-10}		                       
							   &\multirow{2}{*}{ $mpACO^{0.7s}$}  & $f$                &&&&&&&\\
							   &                                 & {\bf run-time (s)} &&&&&&&\\		                       
		\midrule
		\multirow{6}{*}{$2.0$} &\multirow{2}{*}{ $mpShims^{0.7s}$}& $f$                & 11.31 & 6.29  & 5.54  & 5.83  & 5.05  & 10.63 &   \\
		                       &                                 & {\bf run-time (s)} & 2     & 14    & 34    & 106   & 477   & 2417  &   \\
		\cmidrule{2-10}
		                       &\multirow{2}{*}{ $mpACO^{60s}$}   & $f$                &&&&&&&\\
		                       &                                 & {\bf run-time (s)} &&&&&&&\\
		\cmidrule{2-10}		                       
		                       &\multirow{2}{*}{ $mpACO^{0.7s}$}  & $f$                &&&&&&&\\
							   &                                 & {\bf run-time (s)} &&&&&&&\\
		\bottomrule

	\end{tabular}
\textsuperscript{The numbers 0.7s and 60s as superscript on the methods names represent the time limit per node.}	
\normalsize
\end{table}
